FinalManuscript_DISCS_UG

### 2019-03-05 parts/03_methodology_02nonlinearintensitytransformations.tex
Ch 3 updated

In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses). We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
\begin{align}
	\label{eq:scaledquadraturech3}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.

>>>>

In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses). We have derived a closed form approximation in Appendix \ref{sec:logarithm_approximation}.
\begin{align}\label{eq:optimal_log_approximation_ch3}
	\begin{split}
		&\log\left(1+x\right) \\
		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
		&+ \log{16}.
	\end{split}
\end{align}

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{chap:logarithm_approximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.

### 2019-03-05 parts/08_appendices_b_numericalapproximations_updated.tex
Ch 3 updated

\chapter{Logarithm Approximation}
Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments. Several such approaches include CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms~\cite{walther_cordic_2000}, as well as minimax polynomials, which are determined numerically using the Remez algorithm~\cite{harrison_computation_1999}. These algorithms, while efficient, rely on table lookups, which cannot be done in a privacy-preserving system where the function arguments cannot be directly determined.

>>>>

\chapter{LOGARITHM APPROXIMATION}
\label{chap:logarithm_approximation}
Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments. Several such approaches include CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms~\cite{walther_cordic_2000}, as well as minimax polynomials, which are determined numerically using the Remez algorithm~\cite{harrison_computation_1999}. These algorithms, while efficient, rely on table lookups, which cannot be done in a privacy-preserving system where the function arguments cannot be directly determined.
